taxadb: A High-Performance Local Taxonomic Database Interface

### 2019-12-03 paper/manuscript.Rmd
Fix provider table.

```{r echo = FALSE, results = "asis"}
tibble(provider = c("Integrated Taxonomic Information System, @itis",
                                 "National Center for Biological Information's Taxonomy database, @ncbi",
                                 "Catalogue of Life, @col",
                                 "Global Biodiversity Information Facility Taxonomic Backbone, @gbif",
                                 "FishBase, @fishbase",
                                 #"SeaLifeBase",
                                 "Wikidata, @jorrit", "Open Tree Taxonomy, @Rees2017",
                                 "International Union for Conservation of Nature and Natural Resources, @iucn"),
                    abbreviation = c("itis", "ncbi", "col", "gbif", "fb", #"slb",
                                     "wd", "ott", "iucn"),
                    total_identifiers = map(abbreviation, 
                                            ~taxa_tbl(.x) %>% 
                                              select(acceptedNameUsageID) %>% pull() %>% n_distinct())
) %>% knitr::kable(format = "markdown")

>>>>

```{r echo = FALSE, results = "asis"}
# #provider descriptions
desc <- c(itis = "originally formed to standardize taxonomic name usage across many agencies in the United States federal government",
          ncbi = "nomenclature for sequences in the International Nucleotide Sequence Database Collaboration database",
          col = "comphrehensive taxonomic effort, includes some other providers (e.g. itis)",
          gbif = "taxonomic backbone of the GBIF database, assembled from other sources including COL",
          fb = "nomenclature for global database of fishes",
          wd = "",
          ott = "comphrenesive tree of life based on phylogenetic trees and taxonomic data",
          iucn = "taxonomy for classification of species status")

tibble(provider = c("Integrated Taxonomic Information System, (ref:@itis)",
                                 "National Center for Biological Information's Taxonomy database, @ncbi",
                                 "Catalogue of Life, @col",
                                 "Global Biodiversity Information Facility Taxonomic Backbone, @gbif",
                                 "FishBase, @fishbase",
                                 #"SeaLifeBase",
                                 "Wikidata, @jorrit", "Open Tree Taxonomy, @Rees2017",
                                 "International Union for Conservation of Nature and Natural Resources, @iucn"),
                    abbreviation = c("itis", "ncbi", "col", "gbif", "fb", #"slb",
                                     "wd", "ott", "iucn"),
                    total_identifiers = map(abbreviation,
                                            ~taxa_tbl(.x) %>%
                                              select(acceptedNameUsageID) %>% pull() %>% n_distinct()),
                    description = desc
) %>%
  knitr::kable(format = "latex", col.names = c("Provider", "Abbreviation", "Number of \nIdentifiers", "Description"), escape = FALSE) %>%
  kable_styling(latex_options="scale_down") %>%
  kableExtra::column_spec(1, width = "5cm") %>%
  kableExtra::column_spec(4, width = "10cm")
